---
title: "Project proposal"
author: "Too Legit to Overfit"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
library(pander)
```

```{r load-data, message = FALSE}
board_games <- read_csv("../data/board_games.csv")
```

## 1. Introduction

The dataset we are looking at is a collection of board games from Board Game Geeks, which is a crowd-sourced board game review platform. The variables in the dataset are:

 - `game_id` - Unique game identifier
 - `description` - A paragraph of text describing the game
 - `image` - URL image of the game
 - `max_players` - Maximum recommended players
 - `max_playtime` - Maximum recommended playtime (min)
 - `min_age` - Minimum recommended age
 - `min_players` - Minimum recommended players
 - `min_playtime` - Minimum recommended playtime (min)
 - `name` - Name of the game
 - `playing_time` - Average playtime
 - `thumbnail` - URL thumbnail of the game
 - `year_published` - Year game was published
 - `artist` - Artist for game art
 - `category` - Categories for the game (separated by commas)
 - `compilation` - If part of a multi-compilation - name of compilation
 - `designer` - Game designer
 - `expansion` - If there is an expansion pack - name of expansion
 - `family` - Family of game - equivalent to a publisher
 - `mechanic` - Game mechanic - how game is played, separated by comma
 - `publisher` - Company/person who published the game, separated by comma
 - `average_rating` - Average rating on Board Games Geek (1-10)
 - `users_rated` - Number of users that rated the game
 
We would like to use this dataset to analyse the differences between different categories of board game, in terms of playtime, popularity, and ratings.

## 2. Data

```{r dimensions}
glimpse(board_games)
```

## 3. Data analysis plan

We will try to look for correlations between category and popularity, number of ratings, and playtime. The most common categories are

```{r popular-categories}
popular_categories <- board_games %>%
  mutate(categories = str_split(category, ",")) %>%
  pull(categories) %>%
  unlist %>%
  as_tibble %>%
  count(value) %>%
  arrange(desc(n)) %>%
  head(6)

popular_categories %>%
  pander
```
