---
title: "Bruce's little playground"
output:
  html_document:
    theme: journal
    highlight: pygments
---

## Setup

```{r load-packages, message = FALSE}
library(tidyverse)
library(tidymodels)
library(here)
library(pander)
```

```{r read-data, message = FALSE}
board_games <- read_csv(here("data/board_games.csv"))
```

```{r r-squared, echo = FALSE}
display_r_squared <- function(fit) {
  paste0(
    "$$R^2=",
    round(glance(fit)$r.squared[1], 3),
    ",R_{adj}^2=",
    round(glance(fit)$adj.r.squared[1], 3),
    ".$$"
  )
}
```

## Year Published vs Rating

Here we see that average ratings have an overall upwards trend,
with a brief plateau from 1980 to 2000 and then a sharp rise.
This seems to suggest that the preference of the Board Game Geek community
is more toward more recent games than older ones,
and possibly that board games fall out of favour as they age,
although as we have no past ratings data there is no way to verify this.

```{r year-published-rating, message = FALSE}
board_games %>%
  group_by(year_published) %>%
  summarise(rating = mean(average_rating)) %>%
  ggplot(aes(
    x = year_published,
    y = rating
  )) +
  geom_line() +
  geom_smooth() +
  theme_minimal() +
  labs(
    x = "Year Published",
    y = "Rating"
  )
```

Fitting a linear regression we can see that
the year a game was published does affect its ratings,
but it is far from completely explaining it.

```{r year-published-rating-fit}
year_published_rating_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(average_rating ~ year_published, data = board_games)
```

`r display_r_squared(year_published_rating_fit)`

## Year Published vs Number of Ratings

This graph shows us that the number of ratings a game has
is fairly independent of the year that game was published,
with the exception of a dip around 1980.

```{r year-published-users-rated, message = FALSE}
board_games %>%
  group_by(year_published) %>%
  summarise(users = mean(users_rated)) %>%
  ggplot(aes(
    x = year_published,
    y = users
  )) +
  geom_line() +
  geom_smooth() +
  theme_minimal() +
  labs(
    x = "Year Published",
    y = "Number of Ratings"
  )
```

The spike at 1959 can be explained by a few games,
namely *Risk* and *Diplomacy*,
having very high numbers of ratings and
there not being many other games realeased that year.

```{r}
board_games %>%
  filter(
    year_published == 1959
  ) %>%
  arrange(desc(users_rated)) %>%
  select(name, users_rated, year_published) %>%
  pander()
```

The coefficient of determination of our regression,
as well as our graph,
show us that year of publication
is not a good predictor of number of ratings.

```{r year-published-users-rated-fit}
year_published_users_rated_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(users_rated ~ year_published, data = board_games)
```

`r display_r_squared(year_published_users_rated_fit)`

## Most Popular Categories Over Time

First, we find the most popular categories overall.

```{r popular-categories}
board_games_splitcats <- board_games %>% 
  mutate(categories = str_split(category, ","))

popular_categories <- board_games_splitcats %>%
  pull(categories) %>%
  unlist %>%
  as_tibble %>%
  count(value) %>%
  arrange(desc(n)) %>%
  head(6) %>%
  pull(value)
```

Next, we find all of the games in each of these categories.
We are okay with duplicate rows,
as if a game is in two of the most popular categories
we want it to be accounted for in both categories.

```{r popular-games, message = FALSE}
board_games_empty <- board_games_splitcats %>%
  filter(FALSE)
board_games_popcats <- board_games_empty

for (c in popular_categories) {
  board_games_popcats <- full_join(
    board_games_popcats,
    board_games_splitcats %>%
      filter(map_lgl(categories, ~c %in% .x)) %>%
      mutate(category = c)
  )
}
```

Finally, we can plot the popularity of each category over time.
Popularity, here, refers to the number of board games in each category
as this is analogous to popularity among board game manufacturers.

```{r popular-categories-year-published, message = FALSE}
board_games_popcats %>%
  group_by(category, year_published) %>%
  summarise(count = n()) %>%
  ggplot(aes(
    x = year_published,
    y = count,
    color = category
  )) +
  geom_line() +
  theme_minimal() +
  labs(
    x = "Year Published",
    y = "Number of Games",
    color = "Category"
  )
```

We can see here that the number of games has an upward trend.
For one, after about 1990,
card games start to rise far above the others in terms of popularity.
This may be because with the growing popularity of the internet,
it became much easier for people to make and share their own card games.
Also, around 1970, the number of wargames drastically increased,
becoming noticeably more popular than every other category
until being overtaken by card games around 2010
and then all the other popular categories more recently.
