---
title: "Bruce's little playground"
output:
  html_document:
    theme: journal
    highlight: pygments
---

## Setup

```{r load-packages, message = FALSE}
library(tidyverse)
library(here)
```

```{r read-data, message = FALSE}
board_games <- read_csv(here("data/board_games.csv"))
```

## Year Published vs Rating

Here we see that average ratings have an overall upwards trend, with a brief plateau from 1980 to 2000 and then a sharp rise. This seems to suggest that the preference of the Board Game Geek community is more toward more recent games than older ones, and possibly that board games fall out of favour as they age, although as we have no past ratings data there is no way to verify this.

```{r year-published-rating, message = FALSE}
board_games %>%
  group_by(year_published) %>%
  summarise(rating = mean(average_rating)) %>%
  ggplot(aes(
    x = year_published,
    y = rating
  )) +
  geom_line() +
  geom_smooth() +
  theme_minimal() +
  labs(
    x = "Year Published",
    y = "Rating"
  )
```

## Year Published vs Number of Ratings

Here we can see that the number of ratings on games older than 1980 have almost no ratings in comparison to more recent games, where we see exponential growth in users rated. This shows us that more recent games are much more reviewed than those before 1980. So it is clear that not only are older games less well rated, they are also rated by fewer people.

```{r year-published-users-rated, message = FALSE}
board_games %>%
  group_by(year_published) %>%
  summarise(users = sum(users_rated)) %>%
  ggplot(aes(
    x = year_published,
    y = users
  )) +
  geom_line() +
  geom_smooth() +
  theme_minimal() +
  labs(
    x = "Year Published",
    y = "Number of Ratings"
  )
```