---
title: "Connor's Testing with Categories"
output: github_document
---

basic setup :)
  
```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
library(pander)
library(here)
library(tidymodels)
```

```{r read-data, message = FALSE}
board_games <- read_csv(here("data/board_games.csv"))
```
Totally not stealing from the proposal

```{r popular-categories}
board_games_splitcats <- board_games %>% 
  mutate(categories = str_split(category, ","))

popular_categories <- board_games_splitcats %>%
  pull(categories) %>%
  unlist %>%
  as_tibble %>%
  count(value) %>%
  arrange(desc(n)) %>%
  head(6)

popular_categories %>%
  pander

popular_categories <- pull(popular_categories, value)
```

Just looking at how many damn rows we have here

```{r filter-top-cats-alt}
board_games_topcats <- board_games_splitcats %>% 
  filter(map_lgl(categories, ~any(popular_categories %in% .x)))
```

We can investigate the changes in quality of different categories of games. For example, investigating how the quality of board games in the six most common categories changes over time. As a measure of quality, we use the mean rating given to a game in that category (that is, the sum of all ratings in a category (in a given year) divided by the total number of such ratings). 

```{r top-cats-over-time, message = FALSE, warning = FALSE}
av_annual_rating <- function(df, cat = NULL) {
  {if(!is.null(cat)) {
    df %>% filter(map_lgl(categories, ~cat %in% .x))
  } else {
    df
  }} %>% 
  group_by(year_published) %>% 
  summarise(av_annual_rating = sum(average_rating * users_rated) / sum(users_rated))
}
# finds average rating (of a category (cat) if given) of board games in dataframe given (df) for each year in which a board game of that category was published. Output is a dataframe. df must have columns `year published`, `categories` (a `list` of categories), `average_rating` and `year_published`. 

cats <- map(popular_categories, ~av_annual_rating(df = board_games_topcats, cat = .))

cat_ratings <- reduce(cats, ~full_join(.x,.y, by = "year_published")) %>% 
  arrange(year_published)

if(any(is.na(popular_categories))) {
  popular_categories[[which(is.na(popular_categories))]] <- "not_categorised"
} 

names(cat_ratings) <- c("year_published", popular_categories)
```

```{r top-cats-over-time-plot, warning = FALSE}
cat_ratings %>% 
  pivot_longer(cols = 2:ncol(cat_ratings), names_to = "category", values_to = "av_rating") %>% 
  ggplot(aes(x = year_published, y = av_rating, colour = category)) + 
  geom_line() +
  facet_wrap(~ category) +
  labs(
    x = "Year published", 
    y = "Mean annual category rating", 
    colour = "Category", 
    title = "Average ratings of the 6 most popular game categories by year published"
  ) + 
  scale_color_viridis_d() +
  theme_minimal()
```

Looking at this we can see that there is a trend in each category that the annual average rating increases over time, so this might be cool to look into. However next i'll look into the correlation coefficients of each category and the average rating if I can work out how to do that.

```{r top-cats-and-correlations}

```