---
title: "users_rated"
author: "Arjun NR"
date: "11/21/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

## Loading packages
```{r load packages}
library(tidyverse)
library(broom)
library(pander)
library(here)
library(tidymodels)
library(fitdistrplus)
```

## Relevant work from proposal
```{r load-data, message = FALSE}
board_games <- read_csv(here("data/board_games.csv"))
```

```{r popular-categories, include = FALSE}
board_games_splitcats <- board_games %>% 
  mutate(categories = str_split(category, ","))

popular_categories <- board_games_splitcats %>%
  pull(categories) %>%
  unlist %>%
  as_tibble %>%
  count(value) %>%
  arrange(desc(n)) %>%
  head(6)
```

```{r no_ratings-v-rating, warning = FALSE}
board_games_splitcats %>%
  ggplot() +
  geom_point(aes(x = users_rated, y = average_rating), alpha = 0.5) +
  scale_x_log10() +
  labs(
  x = "Number of ratings",
  y = "Average ratings",
  title = "Number of ratings against average rating"
  )
```

This plot suggests that games with more ratings tend to have an average rating closer to just under 7.5. However, this may be because there are more games with a rating of 7.5, which increases the likelihood that there will be a game with particularly a large number of ratings. To analyze this further, we will need to eliminate the effect of this confounding variable (number of games with a given rating) to properly analyze the relationship between the two variables. 

## Further work

```{r plus-x-y-densities}
board_games_splitcats %>%
  ggplot() +
  geom_point(aes(x = users_rated, y = average_rating), alpha = 0.05) +
  geom_density(aes(x = users_rated, y = (..scaled.. * 5)), colour = "red") +
  geom_density(aes(x = (..scaled.. * 1e4), y = average_rating), colour = "orange") +
  scale_x_log10() +
  labs(
  x = "Number of ratings",
  y = "Average ratings",
  title = "Number of ratings against average rating", 
  subtitle = "Showing density plots of x and y overlayed"
  ) + 
  scale_colour_viridis_c()
  # xlim(NA, 20000)
```

```{r av-n-rating-model}
set.seed(314159)
bg_split <- initial_split(board_games_splitcats, prop = 0.8)
train_data <- training(bg_split)
test_data <- testing(bg_split)

bg_fit <- linear_reg() %>% 
  set_engine("lm") %>% 
  fit(average_rating ~ log(users_rated), data = board_games_splitcats)

predict(bg_fit, test_data) %>% 
  bind_cols(test_data %>% dplyr::select(average_rating, users_rated, name))

# YET TO EVALUATE PERFORMANCE
```


```{r 3d-plot-n_rate-avge-year, eval=FALSE}
library(plotly)

board_games_splitcats %>% 
  plot_ly(x = ~users_rated, y = ~average_rating, z = ~year_published, type = "scatter3d", mode = "markers", marker = list(color = ~year_published, colorscale = c('#FFE1A1', '#683531'), showscale = TRUE), size = 1, opacity = 0.1)
# plot_ly(x=temp, y=pressure, z=dtime, type="scatter3d", mode="markers", color=temp)
```

```{r avge_rating-dist-models}
my_data <- board_games_splitcats$average_rating
descdist(my_data, discrete=FALSE, boot=500)

fit <- function(data, distr) {
  fit <- fitdist(data, distr)
  
  print(summary(fit))
  
  return(fit)
}

fit_n  <- fit(my_data, "norm")
fit_ln  <- fit(my_data, "lnorm")
fit_l  <- fit(my_data, "logis")
fit_g  <- fit(my_data, "gamma")

# Following code inspired by http://www.di.fc.ul.pt/~jpn/r/distributions/fitting.html

plot.legend <- c("normal", "lognormal", "logistic", "gamma")

denscomp(list(fit_n, fit_ln, fit_l, fit_g), legendtext = plot.legend, plotstyle = "ggplot") + theme_minimal()

cdfcomp(list(fit_n, fit_ln, fit_l, fit_g), legendtext = plot.legend, plotstyle = "ggplot") + theme_minimal()

qqcomp(list(fit_n, fit_ln, fit_l, fit_g), legendtext = plot.legend, plotstyle = "ggplot") + theme_minimal()

ppcomp(list(fit_n, fit_ln, fit_l, fit_g), legendtext = plot.legend, plotstyle = "ggplot") + theme_minimal()

gofstat(list(fit_n, fit_ln, fit_g, fit_l), fitnames = c("norm", "lnorm", "gamma", "logis"))
```

```{r avge_rating-dist-plot}
sech <- function(x) {
  1 / cosh(x)
}

logis <- function(x, u, s) {
  y <- (1 / (4 * s)) * (sech((x - u) / (2 * s)))^2
  return(y)
}
# inspired by code from https://sebastiansauer.github.io/plotting_s-curve/

logis_av_rating <- function(x) {
  logis(x, fit_l$estimate[1], fit_l$estimate[2])
}

board_games_splitcats %>% 
  ggplot(aes(x = average_rating)) + 
  geom_density() + 
  stat_function(
    fun = dnorm, 
    args = list(
      mean = fit_n$estimate[1], 
      sd = fit_n$estimate[2]
    ), 
    colour = "red", 
    alpha = 0.5
  ) + 
  stat_function(fun = logis_av_rating, colour = "orange", alpha = 0.5) + 
  theme_minimal() + 
  labs(
    title = "Fitting distributtions to distribution of average ratings", 
    subtitle = "red = normal; orange = logistic"
  )
```

