---
title: "How do Certain Factors Affect the Ratings of Boardgames?"
subtitle: "Too Legit to Overfit"
author: "Archie Cannon, Arjun Nanning Ramamurthy, Bruce McPhail, Connor Williams"
institute: "University of Edinburgh"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightLines: true
      countIncrementalSlides: false
---

<style type="text/css">
@import url('https://fonts.googleapis.com/css2?family=Inconsolata&family=Merriweather&display=swap');
body, h1, h2, h3, h4, h5, h6 {
	font-family: 'Merriweather', serif;
}
.remark-code.remark-inline-code {
	font-family: 'Inconsolata', monospace;
}
.remark-slide-number {
  display: none;
}
</style>

```{r load-packages, include = FALSE}
library(tidyverse)
library(tidymodels)
library(knitr)
library(here)
library(xaringanthemer)
library(fitdistrplus)
library(scales)
```

```{r setup, include = FALSE}
opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```

```{r r-squared, echo = FALSE}
display_r_squared <- function(fit) {
  paste0(
    "$R^2=",
    round(glance(fit)$r.squared[1], 3),
    ",R_{adj}^2=",
    round(glance(fit)$adj.r.squared[1], 3),
    ".$"
  )
}
```

```{r load-data, include = FALSE}
board_games <- read_csv(here("data/board_games.csv"))
```

```{r glimpse, echo = FALSE}
glimpse(board_games)
```

---

## Categories

```{r popular-categories, echo = FALSE}
board_games_splitcats <- board_games %>% 
  mutate(categories = str_split(category, ","))

popular_categories <- board_games_splitcats %>%
  pull(categories) %>%
  unlist %>%
  as_tibble %>%
  count(value) %>%
  arrange(desc(n)) %>%
  head(6)

popular_categories %>%
	rename(
		"Category" = value,
		"Number of Games" = n
	) %>%
  kable()

popular_categories <- pull(popular_categories, value)
```

---

```{r filter-top-cats-alt, echo = FALSE, warning = FALSE}
board_games_topcats <- board_games_splitcats %>% 
  filter(map_lgl(categories, ~any(popular_categories %in% .x)))
```

```{r top-cats-over-time, echo = FALSE, message = FALSE, warning = FALSE}
av_annual_rating <- function(df, cat = NULL) {
  {if(!is.null(cat)) {
    df %>% filter(map_lgl(categories, ~cat %in% .x))
  } else {
    df
  }} %>% 
  group_by(year_published) %>% 
  summarise(av_annual_rating = sum(average_rating * users_rated) / sum(users_rated))
}

cats <- map(popular_categories, ~av_annual_rating(df = board_games_topcats, cat = .))

cat_ratings <- reduce(cats, ~full_join(.x,.y, by = "year_published")) %>% 
  arrange(year_published)

if(any(is.na(popular_categories))) {
  popular_categories[[which(is.na(popular_categories))]] <- "not_categorised"
} 

names(cat_ratings) <- c("year_published", popular_categories)
```

```{r top-cats-over-time-plot, echo = FALSE, message = FALSE, warning = FALSE}
cat_ratings %>% 
  pivot_longer(cols = 2:ncol(cat_ratings), names_to = "category", values_to = "av_rating") %>% 
  ggplot(aes(x = year_published, y = av_rating, colour = category)) + 
  geom_line() +
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(~ category) +
  labs(
    x = "Year published", 
    y = "Mean annual category rating", 
    colour = "Category",
    title = "Average ratings plotted over year published",
    subtitle = "Faceted by the 6 most popular categories"
  ) + 
  theme_minimal()
```

---

```{r predicted-rating-residuals, echo = FALSE, warning = FALSE, message = FALSE}
board_games_empty <- board_games_splitcats %>%
  filter(FALSE)
board_games_popcats <- board_games_empty

for (c in popular_categories) {
  board_games_popcats <- full_join(
    board_games_popcats,
    board_games_splitcats %>%
      filter(map_lgl(categories, ~c %in% .x)) %>%
      mutate(category = c)
  )
}

cat_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(average_rating ~ category, data = board_games_popcats)

cat_fit_aug <- augment(cat_fit$fit)

ggplot(cat_fit_aug, mapping = aes(x = .fitted, y = .resid)) +
  geom_point(alpha = 0.5, aes(color = category)) +
  geom_hline(yintercept = 0, color = "gray", lty = "dashed") +
  labs(x = "Predicted rating", y = "Residuals",
       title = "Plot of the residuals using only the 6 categories") +
  theme_minimal()
```

Note that each of these vertical lines represents one of the 6 categories.

---

### Model

```{r looking-at-rsquared, echo = FALSE}
tidy(cat_fit)
```

---

## Year Published

```{r year-published-rating, echo = FALSE, message = FALSE}
board_games %>%
  group_by(year_published) %>%
  summarise(rating = mean(average_rating)) %>%
  ggplot(aes(
    x = year_published,
    y = rating
  )) +
  geom_line() +
  theme_minimal() +
  labs(
    x = "Year Published",
    y = "Rating"
  )
```

---

```{r year-published-rating-fit, echo = FALSE}
year_published_rating_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(average_rating ~ year_published, data = board_games)
```

```{r year-published-rating-line, echo = FALSE, message = FALSE}
board_games %>%
  group_by(year_published) %>%
  summarise(rating = mean(average_rating)) %>%
  ggplot(aes(
    x = year_published,
    y = rating
  )) +
  geom_line() +
	geom_smooth(method = "lm", se = FALSE) +
  theme_minimal() +
  labs(
    x = "Year Published",
    y = "Rating"
  )
```

$`r display_r_squared(year_published_rating_fit)`$

---

## Playing time

```{r playing-time-plot, echo = FALSE, message = FALSE, warning = FALSE}
board_games %>%
  filter(playing_time != 0) %>%
  ggplot(aes(playing_time, average_rating)) +
  geom_point(alpha = 0.6) +
  scale_x_log10() +
  theme_minimal() +
  theme(plot.margin = unit(c(0,1,0,0), "cm")) +
  labs(title = "Average rating against average playing time", x = "Average playing time", y = "Average Rating") 
```

```{r playing-time-model, include = FALSE}
board_games <- board_games %>%
  filter(playing_time != 0, min_playtime != 0)

set.seed(1116)

games_split <- initial_split(board_games, prop = 0.8)
train_data <- training(games_split)
test_data <- testing(games_split) 

games_lm_mod <- linear_reg() %>%
  set_engine("lm")

games_play_recipe <- recipe(average_rating ~ playing_time, data = train_data) %>%
  step_log(all_predictors())

games_play_workflow <- workflow() %>%
  add_model(games_lm_mod) %>%
  add_recipe(games_play_recipe)

games_play_fit <- games_play_workflow %>% 
  fit(data = train_data)

games_play_all_recipe <- recipe(
  average_rating ~ playing_time + min_playtime,
  data = train_data
  ) %>%
  step_log(all_predictors())

games_play_all_workflow <- workflow() %>%
  add_model(games_lm_mod) %>%
  add_recipe(games_play_all_recipe)

games_play_all_fit <- games_play_all_workflow %>%
  fit(data = train_data)

games_play_pred <- predict(games_play_fit, test_data) %>%
  bind_cols(test_data)

games_play_all_pred <- predict(games_play_all_fit, test_data) %>%
  bind_cols(test_data)

predict_both <- games_play_all_pred %>%
  mutate(.pred_all = .pred, .keep = "unused") %>%
  right_join(games_play_pred) %>%
  dplyr::select(.pred, .pred_all, average_rating, everything())

set.seed(450)

folds <- vfold_cv(train_data, v = 5)

set.seed(451)

games_play_fit_rs <- games_play_workflow %>%
  fit_resamples(folds)

games_play_all_fit_rs <- games_play_all_workflow %>%
  fit_resamples(folds)
```

---

```{r playing-time-model-graph, echo = FALSE}
games_play_pred %>%
  ggplot(aes(x = playing_time)) +
  geom_point(aes(y = average_rating)) +
  geom_line(aes(y = .pred), colour = "red") +
  scale_x_log10() +
  theme_minimal() +
  labs(title = "Average rating against average playing time", x = "Average Playing Time", y = "Average Rating")
```

---

### Model statistics

### Slopes

Single variable: $`r round(tidy(games_play_fit)$estimate[2], 3)`$.

Double variable:
`playing_time`: $`r round(tidy(games_play_all_fit)$estimate[2], 3)`$,
`min_playtime`: $`r round(tidy(games_play_all_fit)$estimate[3], 3)`$.

### RMSE

Single variable:
training: $RMSE = `r round(rmse(games_play_pred, average_rating, .pred)$.estimate[1], 3)`$,
test: $RMSE = `r round(collect_metrics(games_play_fit_rs)$mean[1], 3)`$.

Double variable:
training: $RMSE = `r round(rmse(games_play_all_pred, average_rating, .pred)$.estimate[1], 3)`$,
test: $RMSE = `r round(collect_metrics(games_play_all_fit_rs)$mean[1], 3)`$.

### R Squared

Single variable: `r display_r_squared(games_play_fit %>% pull_workflow_fit())`

Double variable: `r display_r_squared(games_play_all_fit %>% pull_workflow_fit())`

---

## Users rated

```{r av-against-num-plots, echo = FALSE, message = FALSE}
# average_rating against users_rated
board_games_splitcats %>%
  ggplot() +
  geom_point(aes(x = users_rated, y = average_rating), alpha = 0.1) +
  labs(
  x = "Number of ratings",
  y = "Average ratings",
  title = "Average rating against number of ratings",
  subtitle = "Each point represents one board game"
  ) + 
  scale_x_log10() +
  theme_minimal()
```

---

```{r avge_rating-dist-models, include = FALSE}
my_data <- board_games_splitcats$average_rating

fitd <- function(data, distr) {
  fitteddist <- fitdist(data, distr)
  
  print(summary(fitteddist))
  
  return(fitteddist)
}

fit_n  <- fitd(my_data, "norm")
```

```{r avge_rating-dist-plot, echo = FALSE, message = FALSE}
board_games_splitcats %>% 
  ggplot(aes(x = average_rating)) + 
  geom_density() + 
  stat_function(
    fun = dnorm, 
    args = list(
      mean = fit_n$estimate[1], 
      sd = fit_n$estimate[2]
    ), 
    colour = "red", 
    alpha = 0.5
  ) + 
  theme_minimal() + 
  labs(
    title = "Fitting distributions to distribution of average ratings", 
    subtitle = "Fitted normal distribution in red",
    x = "Average rating",
    y = "Density"
  )
```

```{r normal, echo = FALSE}
display_normal <- function(mean, sd) {
  paste0(
    "$$Y\\sim N(",
    round(mean, 3),
    ",",
    round(sd, 3),
    "^2)",
    ".$$"
  )
}
```

The normal distribution fitted to `average_rating` is given by `r display_normal(fit_n$estimate[1], fit_n$estimate[2])`

---

## Number of ratings model

```{r av-n-rating-model, echo = FALSE, message = FALSE}
set.seed(314159)
bg_nrate_split <- initial_split(board_games_splitcats, prop = 0.8)
train_data <- training(bg_nrate_split)
test_data <- testing(bg_nrate_split)

bg_nrate_rec <- recipe(
  average_rating ~ users_rated,
  data = train_data
) %>%
  step_log(users_rated)

bg_nrate_model <- linear_reg() %>%
  set_engine("lm")

bg_nrate_wflow <- workflow() %>%
  add_model(bg_nrate_model) %>%
  add_recipe(bg_nrate_rec)

bg_nrate_fit <- bg_nrate_wflow %>%
  fit(data = train_data)

# bg_nrate_fit_tidy <- tidy(bg_nrate_fit)

# Evaluation
set.seed(314159)
folds <- vfold_cv(train_data, v = 5)

bg_nrate_fit_vfold <- bg_nrate_wflow %>%
  fit_resamples(folds)

# Metrics for model fitted to v-fold train data:
train_metrics <- collect_metrics(bg_nrate_fit_vfold)

# predictions and metrics for test data
bg_nrate_pred <- predict(bg_nrate_fit, test_data) %>%
  bind_cols(
    predict(bg_nrate_fit, test_data, type = "pred_int"),
    test_data %>% dplyr::select(average_rating, users_rated, name)
  )

test_rmse <- rmse(bg_nrate_pred, truth = average_rating, estimate = .pred)
test_rsq <- rsq(bg_nrate_pred, truth = average_rating, estimate = .pred)

# tibble of metrics for both train and test data
train_test_metrics <- tribble(
  ~data, ~metric, ~value,
  "train", "rmse", train_metrics$mean[1],
  "train", "rsq", train_metrics$mean[2],
  "test", "rmse", test_rmse$.estimate[1],
  "test", "rsq", test_rsq$.estimate[1],
) %>%
  pivot_wider(names_from = data, values_from = value)

# plot of model on full data
predict(bg_nrate_fit, board_games_splitcats) %>%
  bind_cols(
    predict(bg_nrate_fit, board_games_splitcats, type = "pred_int"),
    board_games_splitcats %>% dplyr::select(average_rating, users_rated, name)
  ) %>%
  ggplot(aes(x = users_rated)) +
  geom_point(aes(y = average_rating), alpha = 0.2) +
  geom_line(aes(y = .pred, colour = "red")) +
  geom_line(aes(y = .pred_upper, colour = "dark red"), linetype = "dashed") +
  geom_line(aes(y = .pred_lower, colour = "dark red"), linetype = "dashed") +
  scale_x_log10() + 
  scale_colour_identity(
    breaks = c("red", "dark red"),
    labels = c("Model", "Prediction interval"),
    guide = "legend"
  ) +
  labs(
    x = "Number of ratings",
    y = "Average rating",
    title = "Average rating modelled against number of ratings"
  ) + 
  theme_minimal()
```

---

## Top 10 highest rated games

```{r top-rated-games, echo = FALSE, message = FALSE}
board_games_splitcats %>% 
  filter(rank(desc(average_rating)) <= 10) %>% 
  arrange(desc(average_rating)) %>% 
  dplyr::select(name, average_rating, year_published) %>% 
	rename(
		"Name" = name,
		"Average Rating" = average_rating,
		"Year Published" = year_published
	) %>%
  kable()
```

---

### Model statistics

```{r nrate-model-stats, echo = FALSE}
train_test_metrics %>% 
  kable()
```

---

## Interesting observations

```{r popular-categories-year-published, echo = FALSE, message = FALSE}
# board_games_splitcats <- board_games %>% 
#   mutate(categories = str_split(category, ","))
# 
# popular_categories <- board_games_splitcats %>%
#   pull(categories) %>%
#   unlist %>%
#   as_tibble %>%
#   count(value) %>%
#   arrange(desc(n)) %>%
#   head(6) %>%
#   pull(value)

board_games_empty <- board_games_splitcats %>%
  filter(FALSE)
board_games_popcats <- board_games_empty

for (c in popular_categories) {
  board_games_popcats <- full_join(
    board_games_popcats,
    board_games_splitcats %>%
      filter(map_lgl(categories, ~c %in% .x)) %>%
      mutate(category = c)
  )
}

board_games_popcats %>%
  group_by(category, year_published) %>%
  summarise(count = n()) %>%
  ggplot(aes(
    x = year_published,
    y = count,
    color = category
  )) +
  geom_line() +
  theme_minimal() +
  labs(
    x = "Year Published",
    y = "Number of Games",
    color = "Category"
  )
```

---

## Conclusions
### Model with all variables

```{r model-with-all, echo = FALSE, message = FALSE}
set.seed(314159)
bg_split <- initial_split(board_games_popcats, prop = 0.8)
train_data <- training(bg_split)
test_data <- testing(bg_split)


bg_rec <- recipe(
  average_rating ~ users_rated + category + year_published + playing_time,
  data = train_data
) %>% 
  step_log(users_rated)

bg_model <- linear_reg() %>% 
  set_engine("lm")

bg_wflow <- workflow() %>% 
  add_model(bg_model) %>% 
  add_recipe(bg_rec)

bg_fit <- bg_wflow %>%
  fit(data = train_data)

bg_fit_tidy <- tidy(bg_fit)

bg_fit_tidy

# Evaluation
set.seed(314159)
folds <- vfold_cv(train_data, v = 5)

bg_fit_vfold <- bg_wflow %>% 
  fit_resamples(folds)

# Metrics for model fitted to v-fold train data: 
bg_train_metrics <- collect_metrics(bg_fit_vfold)

# predictions and metrics for test data
bg_pred <- predict(bg_fit, test_data) %>% 
  bind_cols(
    predict(bg_fit, test_data, type = "pred_int"),
    test_data %>% dplyr::select(average_rating, users_rated, name)
  )

bg_test_rmse <- rmse(bg_pred, truth = average_rating, estimate = .pred)
bg_test_rsq <- rsq(bg_pred, truth = average_rating, estimate = .pred)

bg_train_adj_rsq <- glance(bg_fit %>% pull_workflow_fit)$adj.r.squared[1]

# tibble of metrics for both train and test data
bg_train_test_metrics <- tribble(
  ~data, ~metric, ~value,
  "train", "rmse", bg_train_metrics$mean[1],
  "train", "rsq", bg_train_metrics$mean[2],
  "test", "rmse", bg_test_rmse$.estimate[1],
  "test", "rsq", bg_test_rsq$.estimate[1],
  "train", "adj rsq", bg_train_adj_rsq
) %>% 
  pivot_wider(names_from = data, values_from = value)

bg_train_test_metrics
```

---

# Step 1: Make good games
# Step 2: ???
# Step 3: Profit.
